\appendix
\pagenumbering{roman}
\chapter*{Appendix A: Budget}
\addcontentsline{toc}{chapter}{Appendix A: Budget}
As a physicist, there are a lot of things that I find exciting, e.g. space, quantum mechanics, music, food, sports, skiing etc.. However, economic matters are usually not one of these. And as my fellow physicist colleague, Albert Einstein, once said (according to legend)\footnote{\href{https://www.forbes.com/quotes/195/}{https://www.forbes.com/quotes/195/}}:

\say{\textit{The hardest thing in the world to understand is the income tax}},

the economy usually only result in headache (which is true in many cases). Nevertheless, I am very detailed and planning, so I usually keep a budget. Accordingly, I thought that students alike me (or not alike for that matter, but most students are usually keen about their money), would be interested in how an exchange term in Singapore treats you economically. So, below I provide my result budget from my time in Singapore and Asia. Note that I only show expenses, since these probably are the most interesting and that the exchange rate between SEK and SGD was between 7.4 and 8.2 during my exchange.

Table \ref{tab:my_label} below presents expenses I had before even setting my foot in Singapore, while Table \ref{tab:my_label2} shows expenses during the actual exchange period. As you know by now, I traveled around a lot, and total expenses for my trips each month are presented on the ``Traveling'' row in Table \ref{tab:my_label2}. However, more detailed budgets for each of my trips are given in Tables \ref{tab:travel1} and \ref{tab:travel2}. A small disclaimer is that I'm probably not the most representative person when it comes to expenses. For example, you'll notice that I'm not even close to a shopaholic, but much more closer to a food addict...
\begin{table}[H]
    \centering
    \caption{Budget covering expenses in SEK before the exchange.}
    % \vspace{-0.1cm}
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{|c|c|}
         \toprule 
         \textbf{Expense} & \textsc{Cost [SEK]} \\ \noalign{\global\arrayrulewidth=1.1pt}\hhline{==}
         \noalign{\global\arrayrulewidth=0.4pt}
         Flight tickets (round-trip) & \texttt{- 7\,935} \\ \midrule
         Vaccines (incl. Malaria pills) & \texttt{- 5\,710} \\ \midrule
         Travel Insurance & \texttt{- 2\,521} \\ \midrule
         NTU fees & \texttt{- 3\,304} \\ \midrule
         Student's Pass & \texttt{- 1\,133} \\ \hhline{==} 
         \textbf{Result} & \textbf{\texttt{- 20 603}} \\ \bottomrule
    \end{tabular}
    \label{tab:my_label}
\end{table}

\begin{table}[H]
    \centering
    \caption{Expenses during the exchange period. All costs are given in Singaporean dollars (SGD). Note that Traveling includes all travel expenses, see Tables \ref{tab:travel1} and \ref{tab:travel2} for details.}
    \vspace{0.1cm}
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{|l|c|c|c|c|c|c|}
         \cmidrule[0.9pt]{1-6}
         \textbf{Expense [SGD]} & \textsc{Jan} & \textsc{Feb} & \textsc{Mars} & \textsc{Apr} & \textsc
         {May} & \multicolumn{1}{c}{} \\ \noalign{\global\arrayrulewidth=1.1pt}\hhline{======~}
         \noalign{\global\arrayrulewidth=0.4pt}

         Dorm Rental & \texttt{0} & \texttt{- 2\,578} & \texttt{0} & \texttt{0} & \texttt{0} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}
         
         Groceries and Food &  \texttt{- 359} & \texttt{- 527} & \texttt{- 536} & \texttt{- 555} & \texttt{- 94} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}

         Alcohol &  \texttt{- 59} & \texttt{- 29} & \texttt{- 197} & \texttt{- 190} & \texttt{- 32} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}

         Leisure &  \texttt{- 86} & \texttt{- 144} & \texttt{- 4} & \texttt{0} & \texttt{- 10} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}

         Shopping &  \texttt{- 44} & \texttt{- 217} & \texttt{- 34} & \texttt{- 34} & \texttt{0} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}
         
         Transport in SG & \texttt{- 27} & \texttt{- 56} & \texttt{- 63} & \texttt{- 105} & \texttt{- 66} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}

         Traveling (all incl.) & \texttt{- 1\,248} & \texttt{- 1403} & \texttt{- 1\,555} & \texttt{- 593} & \texttt{- 2\,706} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}
         
         SIM-card & \texttt{- 50} & \texttt{- 12} & \texttt{- 12} & \texttt{- 12} & \texttt{- 12} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}

         Others & \texttt{- 26} & \texttt{- 129} & \texttt{0} & \texttt{- 73} & \texttt{- 17} & \multicolumn{1}{c}{} \\ 
         \cline{6-7}
         \hhline{======~}
         
         \textbf{Result} & \texttt{\textbf{- 1\,899}} & \texttt{\textbf{- 5\,095}} & \texttt{\textbf{- 2\,401}} & \texttt{\textbf{- 1\,562}} & \texttt{\textbf{- 2\,937}} & \texttt{\textbf{- 13\,894}} \\ \bottomrule
    \end{tabular}
    \label{tab:my_label2}
\end{table}
\vspace{-0.1cm}
\begin{table}[H]
    \centering
    \caption{Detailed travel expenses in SGD from January to Mars.}
    \vspace{0.1cm}
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{|l|c|c|c|c|}
        \toprule
        {\large{\textsc{Jan - Mar}}} & \multicolumn{4}{c|}{\textbf{Country}} \\ \cmidrule(lr){1-5} \textbf{Expense [SGD]} & \makecell{\textsc{Thailand} \\ \scriptsize Jan 24th - Feb 2nd} & \makecell{\textsc{Indonesia} \\ \scriptsize Feb 21th - 24th} & \makecell{\textsc{Vietnam} \\ \scriptsize Feb 27th - Mar 7th} & \makecell{\textsc{Hong Kong} \\ \scriptsize Mar 27th - 30th} \\
        \noalign{\global\arrayrulewidth=1.1pt}
        \hhline{=====}
        \noalign{\global\arrayrulewidth=0.4pt}
        Food & \texttt{- 293} & \texttt{- 111} & \texttt{- 436} & \texttt{- 187} \\ \midrule
        Alcohol & \texttt{- 90} & \texttt{- 30} & \texttt{- 83} & \texttt{- 70} \\ \midrule
        Leisure & \texttt{-60} & \texttt{0} & \texttt{- 46} & \texttt{- 37} \\ \midrule
        Shopping & \texttt{0} & \texttt{0} & \texttt{- 186} & \texttt{- 18} \\ \midrule
        Housing & \texttt{- 422} & \texttt{- 52} & \texttt{- 94} & \texttt{- 105} \\ \midrule
        Flight Tickets & \texttt{- 283} & \texttt{0} & \texttt{- 305} & \texttt{- 304} \\ \midrule
        Other Transports & \texttt{- 183} & \texttt{- 94} & \texttt{- 58} & \texttt{- 77} \\ \midrule
        Others & \texttt{0} & \texttt{- 56} & \texttt{0} & \texttt{0} \\ \hhline{=====}
        \textbf{Result} & \texttt{\textbf{- 1\,331}} & \texttt{\textbf{- 344}} & \texttt{\textbf{- 1\,208}} & \texttt{\textbf{- 798}} \\ \bottomrule
    \end{tabular}
    \label{tab:travel1}
\end{table}

\begin{table}[H]
    \centering
    \caption{Detailed travel expenses in SGD from April to June.}
    \vspace{0.1cm}
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{|l|c|c|c|c|}
        \toprule
        %\multirow{2}{*}
        {\large{\textsc{Apr - Jun}}} & \multicolumn{4}{c|}{\textbf{Country}} \\ \cmidrule(lr){1-5} \textbf{Expense [SGD]} & \makecell{\textsc{Laos} \\ \scriptsize May 2nd - 8th} & \makecell{\textsc{Japan} \\ \scriptsize May 8th - 18th} & \makecell{\textsc{South Korea} \\ \scriptsize May 18th - 23rd} & \makecell{\textsc{Taiwan} \\ \scriptsize May 23rd - 28th} \\
        \noalign{\global\arrayrulewidth=1.1pt}
        \hhline{=====}
        \noalign{\global\arrayrulewidth=0.4pt}
        Food & \texttt{- 137} & \texttt{- 473} & \texttt{- 136} & \texttt{- 141} \\ \midrule
        Alcohol & \texttt{- 30} & \texttt{- 89} & \texttt{- 27} & \texttt{- 20} \\ \midrule
        Leisure & \texttt{- 65} & \texttt{- 43} & \texttt{- 133} & \texttt{- 61} \\ \midrule
        Shopping & \texttt{- 20} & \texttt{- 69} & \texttt{- 9} & \texttt{- 68} \\ \midrule
        Housing & \texttt{- 32} & \texttt{- 355} & \texttt{-219} & \texttt{- 234} \\ \midrule
        Flight Tickets & \texttt{- 139} & \texttt{- 334} & \texttt{- 135} & \texttt{- 135} \\ \midrule
        Other Transports & \texttt{- 113} & \texttt{- 236} & \texttt{- 104} & \texttt{- 51} \\ \midrule
        Other Expenses & \texttt{- 84} & \texttt{- 39} & \texttt{- 46} & \texttt{- 35} \\ \hhline{=====}
        \textbf{Result} & \texttt{\textbf{- 620}} & \texttt{\textbf{- 1\,638}} & \texttt{\textbf{- 809}} & \texttt{\textbf{- 745}} \\ \bottomrule
    \end{tabular}
    \label{tab:travel2}
\end{table}

\chapter*{Appendix B: Links and Apps} \label{appB}
\addcontentsline{toc}{chapter}{Appendix B: Links and Apps}
Below, I've listed some useful links and apps that I found useful during my exchange semester. I used many of these on a daily basis, and I'd recommend to download them right away. I've also added some additional scholarships not mentioned in the text that might be worth checking out (although I didn't).

\textbf{Links}
\begin{itemize}
    \item \href{https://aentry.app/events}{Aentry} -- an app to access and buy tickets to various events in Singapore, mostly at nightclubs and bars. Usually students get a discount code for the subscription.
    \item \href{https://www.redbus.sg}{Redbus} -- a website for booking bus tickets in Singapore and Malaysia. For example, I used this to book my bus tickets to Kuala Lumpur and back.
    \item \href{https://12go.asia/en}{12GO} -- a website for booking train, bus, and ferry tickets in Southeast Asia. For example, I used this to book a ferry ticket from Singapore to Batam.
    \item \href{https://www.airbnb.se}{Airbnb}, \href{https://www.booking.com}{Booking}, \href{https://www.agoda.com/sv-se/?ds=eGn8Sjtq6XiLUdOw}{Agoda} -- websites for booking accommodation, among other things, which I used for my trips.
\end{itemize}

\textbf{Apps}
\\[0.25cm]
For navigation, Google Maps and Apple Maps works very well (also for the MRT system). However, some of the apps below are great complements/alternatives to these.
\begin{itemize}
    \item \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/sg/app/grab-taxi-ride-food-delivery/id647268330&ved=2ahUKEwjF8Z-HwM6NAxX3U1UIHRNmCeEQFnoECAsQAQ&usg=AOvVaw0dB-Vqdf1YjwezvtAhQq6H}{Grab} -- basically the Uber (and Foodora) of Southeast Asia.
    \item \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/us/app/ntu-omnibus/id1636457987&ved=2ahUKEwiV0aGN46-KAxWHIxAIHXUHBg0QFnoECBsQAQ&usg=AOvVaw0nbsveDMT3B2KE9kmpcAZ_}{NTU Omnibus} -- an app for the NTU shuttle buses, the best way to dodge a walk in the heat.
    \item \href{https://citymapper.com/ios?cmpage=slash&cmlink=topnav&region_id=dk-copenhagen}{Citymapper} -- an app for navigating public transport in most cities around the world, which becomes very useful when traveling.
    \item \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/sg/app/blackboard/id950424861&ved=2ahUKEwjR5Mj_w4GLAxUSyTgGHSk2PeEQFnoECBAQAQ&usg=AOvVaw2T7qh926fpN6z3PnP8uqkT}{Blackboard} -- essentially the Canvas app used at NTU to access all the material for your courses.
    \item \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/us/app/telegram-messenger/id686449807&ved=2ahUKEwj0ksCUyc2LAxWazDgGHTttEz0QFnoECBYQAQ&usg=AOvVaw3whV8-0yYMcln1v7fxge7f}{Telegram} -- the most popular messaging app in Singapore.
    \item \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/se/app/singpass/id1340660807&ved=2ahUKEwjU8fyHwc6NAxXaIxAIHctlNPIQFnoECB8QAQ&usg=AOvVaw3KrYhfL9kT4bAqZRZ4TscT}{Singpass} -- an app for accessing your Singpass, which is needed for many things in Singapore, such as applying for a Singaporean bank account.
\end{itemize}
\vspace{2cm}
\textbf{Scholarships}
\begin{itemize}
    \item \href{https://www.globalgrant.com}{Global Grant} \\ Great website for finding scholarships in general. They are also responsible for the SOS-scholarship, which I applied for.
    \item \href{https://egefonden.se}{Erik och Göran Ennerfelts Stiftelse} \\ This application closes rather early, my year it was in March, hence why I didn't apply.
    \item \href{https://tmw.wallenberg.org/anslagsguide}{Tekn Dr Marcus Wallenbergs fond för utbildning i internationellt företagande} \\ For this, you need to study for a whole year to apply.
    \item \href{https://wp.hvitfeldtskastiftelsen.se/universitetsstipendium/}{Hvitfeldtska Stiftelsen} \\ From my understanding, you need to have completed high school in Gothenburg to apply for this.
    \item \href{https://stiftelsenrljs.se/hogre-studier/}{Rune Ljungdahls Stiftelse}
    \item \href{https://www.chalmers.se/utbildning/studera-hos-oss/studentliv/stipendier-for-studenter/donationsstipendierna/}{Donationsstipendierna Chalmers}
    \item \href{https://www.uppfostringsfonderna.se}{Uppfostringsfonderna}
    \item \href{https://stiftelsemedel.se/rdman-och-fru-ernst-collianders-stiftelse-fr-vlgrande-ndaml/}{Rådman och fru Ernst Collianders stiftelse}
\end{itemize}
