\appendix
\pagenumbering{roman}
\chapter*{Appendix A: Budget}
\addcontentsline{toc}{chapter}{Appendix A: Budget}
\vspace{-0.1cm}
As a physicist, there are lots of things that I find exciting, e.g., space, quantum mechanics, music, food, sports, skiing etc.. However, economic matters aren't usually one of these. And as my fellow physicist colleague, Albert Einstein, once said (according to legend)\footnote{\href{https://www.forbes.com/quotes/195/}{https://www.forbes.com/quotes/195/}}:

\say{\textit{The hardest thing in the world to understand is the income tax}},

they usually only result in a headache anyway (which often is true). Nevertheless, I'm very detailed and planning, so I always have a budget. Accordingly, I thought that students like me (or not like me, for that matter, though most students are usually keen about their money), would be interested in how an exchange term in Singapore treats you economically. So, below I provide my result budget from my time in Singapore and Asia. Note that the exchange rate SGD/SEK was between 7.4 and 8.2 during my exchange and that I only show expenses, since these probably are the most interesting.

Table \ref{tab:my_label} below presents expenses I had before even setting my foot in Singapore, while Table \ref{tab:my_label2} shows expenses during the actual exchange period. As you know by now, I traveled around a lot, and total expenses for my trips each month are presented on the ``Traveling (all incl.)'' row in Table \ref{tab:my_label2}. However, more detailed budgets for each of my trips are given in Tables \ref{tab:travel1} and \ref{tab:travel2}. Lastly, a small disclaimer is that I'm probably not the most representative person when it comes to spending money. For example, you'll notice that I'm not even close to being a shopaholic -- but much closer to being a food addict...
\begin{table}[H]
    \centering
    \caption{Budget covering expenses in SEK before the exchange.}
    % \vspace{-0.1cm}
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{|c|c|}
         \toprule 
         \textbf{Expense [SEK]} & \textsc{Cost} \\ \noalign{\global\arrayrulewidth=1.1pt}\hhline{==}
         \noalign{\global\arrayrulewidth=0.4pt}
         Flight tickets (round trip) & \texttt{- 7\,935} \\ \midrule
         Vaccines (incl. malaria pills) & \texttt{- 5\,710} \\ \midrule
         Travel insurance & \texttt{- 2\,521} \\ \midrule
         NTU fees & \texttt{- 3\,304} \\ \midrule
         Student's Pass & \texttt{- 1\,133} \\ \hhline{==} 
         \textbf{Result} & \textbf{\texttt{- 20 603}} \\ \bottomrule
    \end{tabular}
    \label{tab:my_label}
\end{table}

\begin{table}[H]
    \centering
    \caption{Expenses during the exchange period. All costs are given in SGD. Note that ``Traveling (all incl.)'' includes all travel expenses, see Tables \ref{tab:travel1} and \ref{tab:travel2} for details.}
    \vspace{0.1cm}
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{|l|c|c|c|c|c|c|}
         \cmidrule[0.9pt]{1-6}
         \textbf{Expense [SGD]} & \textsc{Jan} & \textsc{Feb} & \textsc{Mar} & \textsc{Apr} & \textsc
         {May} & \multicolumn{1}{c}{} \\ \noalign{\global\arrayrulewidth=1.1pt}\hhline{======~}
         \noalign{\global\arrayrulewidth=0.4pt}

         Dorm rental & \texttt{0} & \texttt{- 2\,578} & \texttt{0} & \texttt{0} & \texttt{0} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}
         
         Groceries and food &  \texttt{- 359} & \texttt{- 527} & \texttt{- 536} & \texttt{- 555} & \texttt{- 94} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}

         Alcohol &  \texttt{- 59} & \texttt{- 29} & \texttt{- 197} & \texttt{- 190} & \texttt{- 32} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}

         Leisure &  \texttt{- 86} & \texttt{- 144} & \texttt{- 4} & \texttt{0} & \texttt{- 10} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}

         Shopping &  \texttt{- 44} & \texttt{- 217} & \texttt{- 34} & \texttt{- 34} & \texttt{0} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}
         
         Transport in SG & \texttt{- 27} & \texttt{- 56} & \texttt{- 63} & \texttt{- 105} & \texttt{- 66} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}

         Traveling (all incl.) & \texttt{- 1\,248} & \texttt{- 1403} & \texttt{- 1\,555} & \texttt{- 593} & \texttt{- 2\,706} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}
         
         SIM card & \texttt{- 50} & \texttt{- 12} & \texttt{- 12} & \texttt{- 12} & \texttt{- 12} & \multicolumn{1}{c}{} \\ \cmidrule{1-6}

         Others & \texttt{- 26} & \texttt{- 129} & \texttt{0} & \texttt{- 73} & \texttt{- 17} & \multicolumn{1}{c}{} \\ 
         \cline{6-7}
         \hhline{======~}
         
         \textbf{Result} & \texttt{\textbf{- 1\,899}} & \texttt{\textbf{- 5\,095}} & \texttt{\textbf{- 2\,401}} & \texttt{\textbf{- 1\,562}} & \texttt{\textbf{- 2\,937}} & \texttt{\textbf{- 13\,894}} \\ \bottomrule
    \end{tabular}
    \label{tab:my_label2}
\end{table}
\vspace{-0.1cm}
\begin{table}[H]
    \centering
    \caption{Detailed travel expenses in SGD from January to Mars.}
    \vspace{0.1cm}
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{|l|c|c|c|c|}
        \toprule
        {\large{\textsc{Jan - Mar}}} & \multicolumn{4}{c|}{\textbf{Country}} \\ \cmidrule(lr){1-5} \textbf{Expense [SGD]} & \makecell{\textsc{Thailand \&} \\ \textsc{Malaysia} \\ \scriptsize Jan 24th - Feb 2nd} & \makecell{\textsc{Indonesia} \\ \scriptsize Feb 21th - 24th} & \makecell{\textsc{Vietnam} \\ \scriptsize Feb 27th - Mar 7th} & \makecell{\textsc{Hong Kong} \\ \scriptsize Mar 27th - 30th} \\
        \noalign{\global\arrayrulewidth=1.1pt}
        \hhline{=====}
        \noalign{\global\arrayrulewidth=0.4pt}
        Food & \texttt{- 305} & \texttt{- 111} & \texttt{- 436} & \texttt{- 187} \\ \midrule
        Alcohol & \texttt{- 90} & \texttt{- 30} & \texttt{- 83} & \texttt{- 70} \\ \midrule
        Leisure & \texttt{-60} & \texttt{0} & \texttt{- 46} & \texttt{- 37} \\ \midrule
        Shopping & \texttt{0} & \texttt{0} & \texttt{- 186} & \texttt{- 18} \\ \midrule
        Housing & \texttt{- 422} & \texttt{- 52} & \texttt{- 94} & \texttt{- 105} \\ \midrule
        Flight tickets & \texttt{- 283} & \texttt{0} & \texttt{- 305} & \texttt{- 304} \\ \midrule
        Other transports & \texttt{- 183} & \texttt{- 150} & \texttt{- 58} & \texttt{- 77} \\ \hhline{=====}%\midrule
        %Others & \texttt{0} & \texttt{- 56} & \texttt{0} & \texttt{0} \\ \hhline{=====}
        \textbf{Result} & \texttt{\textbf{- 1\,343}} & \texttt{\textbf{- 343}} & \texttt{\textbf{- 1\,208}} & \texttt{\textbf{- 798}} \\ \bottomrule
    \end{tabular}
    \label{tab:travel1}
\end{table}

\begin{table}[H]
    \centering
    \caption{Detailed travel expenses in SGD from April to June.}
    \vspace{0.1cm}
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{|l|c|c|c|c|}
        \toprule
        %\multirow{2}{*}
        {\large{\textsc{Apr - Jun}}} & \multicolumn{4}{c|}{\textbf{Country}} \\ \cmidrule(lr){1-5} \textbf{Expense [SGD]} & \makecell{\textsc{Laos} \\ \scriptsize May 2nd - 8th} & \makecell{\textsc{Japan} \\ \scriptsize May 8th - 18th} & \makecell{\textsc{South Korea} \\ \scriptsize May 18th - 23rd} & \makecell{\textsc{Taiwan} \\ \scriptsize May 23rd - 28th} \\
        \noalign{\global\arrayrulewidth=1.1pt}
        \hhline{=====}
        \noalign{\global\arrayrulewidth=0.4pt}
        Food & \texttt{- 137} & \texttt{- 473} & \texttt{- 136} & \texttt{- 141} \\ \midrule
        Alcohol & \texttt{- 30} & \texttt{- 89} & \texttt{- 27} & \texttt{- 20} \\ \midrule
        Leisure & \texttt{- 65} & \texttt{- 43} & \texttt{- 133} & \texttt{- 61} \\ \midrule
        Shopping & \texttt{- 20} & \texttt{- 69} & \texttt{- 9} & \texttt{- 68} \\ \midrule
        Housing & \texttt{- 32} & \texttt{- 355} & \texttt{-219} & \texttt{- 234} \\ \midrule
        Flight tickets & \texttt{- 139} & \texttt{- 334} & \texttt{- 135} & \texttt{- 135} \\ \midrule
        Other transports & \texttt{- 113} & \texttt{- 236} & \texttt{- 104} & \texttt{- 51} \\ \midrule
        Others & \texttt{- 84} & \texttt{- 39} & \texttt{- 46} & \texttt{- 35} \\ \hhline{=====}
        \textbf{Result} & \texttt{\textbf{- 620}} & \texttt{\textbf{- 1\,638}} & \texttt{\textbf{- 809}} & \texttt{\textbf{- 745}} \\ \bottomrule
    \end{tabular}
    \label{tab:travel2}
\end{table}

\chapter*{Appendix B: Links and Apps} \label{appB}
\addcontentsline{toc}{chapter}{Appendix B: Links and Apps}
Below, I've listed some useful links and apps that I found useful during my exchange semester. I used many of these on a daily basis, and for the apps, I'd recommend to download them right away. I've also added some additional scholarships not mentioned in the text that might be worth applying for (although I didn't).

\textbf{Links}
\begin{itemize}
    \item \href{https://www.chalmers.se/en/education/your-studies/exchange-studies-and-international-opportunities/exchange-studies/preparing-for-exchange-studies/}{Study plan} -- on this page, under ``Forms and Manuals'', you could download the study plan, which you should fill out and submit to your MSc program's DoS.
    \item \href{https://gem.ntu.edu.sg/index.cfm?FuseAction=Programs.ViewProgramAngular&id=10006}{General coursework information for exchange students} -- contained all the necessary links and information when it came to choosing courses.
    \item \href{https://wish.wis.ntu.edu.sg/pls/webexe/ldap_login.login?w_url=https://wish.wis.ntu.edu.sg/pls/webexe/aus_stars_planner.main}{STARS} -- the NTU course selection system, where you could select courses and study your timetable (only available after you had activated your NTU account).
    \item \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://ntu.facilitiesbooking.com/&ved=2ahUKEwi-k6Pays2LAxUg2TgGHZjtK4sQFnoECAsQAQ&usg=AOvVaw0UI5Z1OVQuEv2rAMKN2LGh}{Booking system for NTU facilities} -- here, you could book study rooms, sports facilities, and other things at NTU. I used this to book table tennis and badminton sessions (login needed).
    \item \href{https://mex.portal.chalmers.se}{Chalmers MEX Portal} -- used to accredit your courses at NTU after your exchange.
    \item \href{https://aentry.app/events}{Aentry} -- a website (and an app) to access and buy tickets to various events in Singapore, mostly at nightclubs and bars.
    \item \href{https://www.redbus.sg}{Redbus} -- a website for booking bus tickets in Singapore and Malaysia. For example, I used this to book my bus tickets to Kuala Lumpur and back.
    \item \href{https://12go.asia/en}{12GO} -- a website for booking train, bus and ferry tickets (among other things) in Southeast Asia. For example, I used this to book ferry tickets from Singapore to Batam and back.
    \item \href{https://www.airbnb.se}{Airbnb}, \href{https://www.booking.com}{Booking}, \href{https://www.agoda.com/sv-se/?ds=eGn8Sjtq6XiLUdOw}{Agoda} -- websites for booking accommodation, among other things (these sites went extremely warm for me before and during my travels).
    \item \href{https://www.ica.gov.sg}{ICA} -- no, not the Swedish supermarket chain, but the Immigration and Checkpoints Authority of Singapore. This was the authority that issued your STP and where you submitted your SGAC when traveling.
\end{itemize}
\newpage
\textbf{Apps}
\begin{itemize}
    \item \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/us/app/google-maps/id585027354&ved=2ahUKEwisooaR7ImOAxUtUlUIHSIjJoMQFnoECAoQAQ&usg=AOvVaw2jT7BmzU1GP-evpK9978cA}{Google} and \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/us/app/apple-maps/id915056765&ved=2ahUKEwj04Nye7ImOAxU9FBAIHfmWCpgQFnoECAoQAQ&usg=AOvVaw2pPxeLW9EBDN3QYaTVb-FJ}{Apple Maps} -- explain themselves, and were great for navigation in Singapore (also for the MRT system) and Asia (except for South Korea).
    \item \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/sg/app/grab-taxi-ride-food-delivery/id647268330&ved=2ahUKEwjF8Z-HwM6NAxX3U1UIHRNmCeEQFnoECAsQAQ&usg=AOvVaw0dB-Vqdf1YjwezvtAhQq6H}{Grab} -- basically the Uber (and Foodora) of Southeast Asia.
    \item \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/us/app/ntu-omnibus/id1636457987&ved=2ahUKEwiV0aGN46-KAxWHIxAIHXUHBg0QFnoECBsQAQ&usg=AOvVaw0nbsveDMT3B2KE9kmpcAZ_}{NTU Omnibus} -- a scheduling app for the NTU bus system, and the ultimate tool for dodging a walk in the heat.
    \item \href{https://citymapper.com/ios?cmpage=slash&cmlink=topnav&region_id=dk-copenhagen}{Citymapper} -- an app for navigating public transport in most cities around the world, which became very useful when traveling.
    \item \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/sg/app/blackboard/id950424861&ved=2ahUKEwjR5Mj_w4GLAxUSyTgGHSk2PeEQFnoECBAQAQ&usg=AOvVaw2T7qh926fpN6z3PnP8uqkT}{Blackboard} -- essentially the Canvas app of NTU, used to access all the material for your courses.
    \item \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/us/app/telegram-messenger/id686449807&ved=2ahUKEwj0ksCUyc2LAxWazDgGHTttEz0QFnoECBYQAQ&usg=AOvVaw3whV8-0yYMcln1v7fxge7f}{Telegram} -- the most popular messaging app in Singapore.
    \item \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/se/app/singpass/id1340660807&ved=2ahUKEwjU8fyHwc6NAxXaIxAIHctlNPIQFnoECB8QAQ&usg=AOvVaw3KrYhfL9kT4bAqZRZ4TscT}{Singpass} -- an app for accessing your Singpass, which was needed for many things in Singapore, such as applying for a Singaporean bank account.
    \item \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/ca/app/roamify-travel-esim-data-call/id6472396976&ved=2ahUKEwi7y9-96omOAxUIJhAIHZvSAG0QFnoECAsQAQ&usg=AOvVaw2EyfUaHaPZfjNMj43MYdyp}{Roamify} -- an app for buying eSIMs with data plans covering most countries in the world, which I used during my trips to Japan, South Korea, and Taiwan. \href{https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://apps.apple.com/us/app/saily-esim-data-for-travel/id6475045151&ved=2ahUKEwj0--rxg5COAxUnQVUIHQuCDZsQFnoECDkQAQ&usg=AOvVaw04URgsyL163pOjndjnyKxH}{Saily} also seems to be a solid option, although I haven't tried it.
\end{itemize}

\textbf{Scholarships}
\begin{itemize}
    \item \href{https://www.globalgrant.com}{Global Grant} \\ Great website for finding scholarships in general. They were also responsible for the SOS-scholarship, which I applied for.
    \item \href{https://egefonden.se}{Erik och Göran Ennerfelts Stiftelse} \\ The application for this closed rather early, for me it was in March, hence why I didn't apply.
    \item \href{https://tmw.wallenberg.org/anslagsguide}{Tekn. Dr. Marcus Wallenbergs fond för utbildning i internationellt företagande} \\ For this, you had to study for a whole year to apply.
    \item \href{https://wp.hvitfeldtskastiftelsen.se/universitetsstipendium/}{Hvitfeldtska Stiftelsen} \\ From my understanding, completion of high school in Gothenburg is required to apply for this.
    \item \href{https://stiftelsenrljs.se/hogre-studier/}{Rune Ljungdahls Stiftelse}
    \item \href{https://www.chalmers.se/utbildning/studera-hos-oss/studentliv/stipendier-for-studenter/donationsstipendierna/}{Donationsstipendierna Chalmers}
    \item \href{https://www.uppfostringsfonderna.se}{Uppfostringsfonderna}
    \item \href{https://stiftelsemedel.se/rdman-och-fru-ernst-collianders-stiftelse-fr-vlgrande-ndaml/}{Rådman och Fru Ernst Collianders Stiftelse}
\end{itemize}
